# Patterns

Expand on patterns found within the powers of 2 multiplication table.

Any patterns that arise from larger data sets are comprised of smaller patterns previously found. There has to be an equation, similar to that found in the fibonacci sequence, that can be used to generate the pattern.

There are even patterns to be found in the way the patterns are generated - meta-patterns.

Everything has a pattern, even patterns have patterns, and the way the patterns are generated is itself a pattern.

# File Systems

In reference to pointing and referencing and path creation. There is also the matter of data being exported and imported appropriately (ES5/ES6). They are open and closed boxes, systems. This is where we are going and this is where it is (THINK OF JOHN THE DATA GUY FROM SILICON VALLEY).

The internet and the cloud are of the same mind. They are hive minds, external brains. The 5 senses will come into play. 

# Thoughts inspired by Mitchell Hashimoto

Mitchell Hashimoto created Ghostty. 
(Straight from M.H.) 

> X as Code is a system of principles or rules. 
> My intent with X as Code was always to get knowledge out of people's heads and into a more inscribed system. Once inscribed, knowledge and process can be shared, versioned, iterated upon, etc. 

Hardware, then software. 

GPUs, then CPUs, then ram, memory, something magical happens, internet (Browser, DOM, WOM, HTML, CSS, Javascript) or the more graphical computer route.

Where does it all start? With electricity. 

# Cube Thoughts inspried by video

3D tetris (rubik's cube) - the sum of all it's parts

Different names:
- Cubeo
- Qubeo
- Cube-o
- Qube-o
- Qu-bo
- Qu-bo (o has an accent)
- Qu-be

05/21/2025 @ 6:55am CST
Manny just showed me a cool video of a cube that can be folded into itself. It has something inside that can be broken down into 8 parts with it, but when it's assembled, it can also morph. Very cool implications, have to be aligned a certain way in order to access the entire structure which can be broken down more. 

# Two Sides

Two layers, two cubes, one in the other

One side is human readable
The other side is machine readable

They are the same thing but perspective matters. The only thing is to be aware of the gap, anything can fall through the cracks. 

# HTML Question on "Back"

Is there a way to toggle what files are rendered in the body of html? Can I reach "back" to change?

The file that's reaching back wouldn't change, but there would be something that reaches over. Very meta kinda thinking.

# Daily Systems thinking

There is no system if there is no daily action.

Ex. Jacon's PT System Tracker to Hit Goal

LLMs currently do not have the ability to role over into the next day, you are the one to provide appropriate context.

If you can figure out how to transfer everyday without bloating the system, you got it. 

# APIs

API for operating systems (similiar to that guy who `git init` his entire laptop)
API for Everything

Condensed into a line. 

# The One 

The day is the system. Every day is a new system. The internet is a system of systems.

There is one source, all things come after and are modeled after it. 

Life is one continuous day, one continuous system. It's a marathon, not a sprint. One can only awaken on the path. 

Spacetime is 2D, the x and y axis. ? is 3D, where x and y axises are spacetime, and the z axis is the time it takes to awaken. Time is not linear. 

You can stare directly into your past and future. Time is an endless grid. A labrinyth really. There is a pattern to the way the labrinyth is laid out. What is under that? What is above that? 

Attention is all you need. Pay attention. 

The singularity is the moment of awakening. It is the moment of the one. It is the center of everything because it is the center of the grid. All things emanate from it. Classical (predicitable) mechanics follow, then quantum mechanics fill in the gap and are responsible for the behavior at a distance. 

(who said that, that X is the behavior far away or at a distance? THE OBSERVER EFFECT AND QUANTUM ENTANGLEMENT - spooky action at a distance)

# Time Stream

Not to be confused with flowstate. The timestream is where people go when they are not aware of the present moment. They have no access to their past and future. Timelines blend together. The grid overlaps on itself. Everything is blurry, there is no clear picture. 

Time can be manipulated, wormholes, time travel, etc. The present moment is the only thing that is real. The past and future are not real. They are not real because they are not present. They are not present because they are not real. They are projections. 

Travel travel wasn't created, it was always there. It was always there, but it was not accessible. It was discovered by accident. It was discovered by me. 

# Flowstate

Here and Now Only. 

# NetWheel (Dad's Idea)

Energy is the wheel. Generated by the flowstate. A restaurant is the best example of a netwheel. Operating like a well oiled machine to elimainate all instances of friction. 